Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
Examples, local state encapsulatoin

\todo[inline]{Put paragraph about memory satisfaction here}
\begin{align*}
  &\memSat{\ms}{W}
    \text{ iff }
    \left\{\begin{aligned}
        &\exists P : \activeReg{W} \rightarrow \HeapSegments \ldotp \\
        &\quad (\hs = \biguplus_{r\in\activeReg{W}}P(r) \text{\footnotesize{ and }} \\
        &\quad \forall r \in \activeReg{W} \ldotp \exists H,s \ldotp\\
        &\qquad W(r) = (\_,s,\_,\_,H) \text{\footnotesize{ and }} \\
        &\qquad \npair[n]{P(r)} \in H(s)(\xi^{-1}(W)))\\
      \end{aligned}\right.
\end{align*}

@@

\section{Examples}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f1: push 1
    fetch $r_1$ $r_\adv$
    scall $r_1$($[]$,$[]$)
    pop $r_1$
    assert $r_1$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a stack-based calling convention.}
  \label{fig:prog-f1}
\end{figure}

\begin{figure}[htbp]
  \centering
\begin{lstlisting}
f2: malloc $r_l$ 1
    store $r_l$ 1
    fetch $r_1$ $\adv$
    call $r_1$($[]$,$[r_l]$)
    assert $r_l$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a calling convention not relyant
    on the stack}
  \label{fig:prog-f2}
\end{figure}

>>>>

\begin{align*}
  &\memSat{\ms}{W}
    \text{ iff }
    \left\{\begin{aligned}
        &\exists P : \activeReg{W} \rightarrow \HeapSegments \ldotp \\
        &\quad (\hs = \biguplus_{r\in\activeReg{W}}P(r) \text{\footnotesize{ and }} \\
        &\quad \forall r \in \activeReg{W} \ldotp \exists H,s \ldotp\\
        &\qquad W(r) = (\_,s,\_,\_,H) \text{\footnotesize{ and }} \\
        &\qquad \npair[n]{P(r)} \in H(s)(\xi^{-1}(W)))\\
      \end{aligned}\right.
\end{align*}

@@

\section{Examples}
In this section, we display how capability safety allows us to prove
local state encapsulation and control-flow integrity properties. For
presentation purposes, we do not formally state the lemmas we
prove. The intere
sted reader can find all the technical details in the
techincal report.

\subsection{Encapsulation of local state} 
The program \texttt{f1} in \figurename~\ref{fig:prog-f1} simply pushes 1 to the
stack, jumps to an adversary using \texttt{scall} and finally asserts
the top value on the stack is 1. If this program is linked up
with an arbitrary adversary that has access to malloc but otherwise only
consists of instructions, then we can show that the assertion never
fails. This shows that the local state of $\texttt{f1}$ is
encapsulated.
\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f1: push 1
    fetch $r_1$ $r_\adv$
    scall $r_1$($[]$,$[]$)
    pop $r_1$
    assert $r_1$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a stack-based calling convention.}
  \label{fig:prog-f1}
\end{figure}

\todo[inline]{give a taste of a proof by giving high-level proof here?
Maybe later for one of the other examples}

In \figurename~\ref{fig:prog-2}, we have \texttt{f2}. \texttt{f2} is
very similar to \texttt{f1}, but instead of using the stack for local
state and the stack-based calling convention, it allocates new memory
for the local state and use a calling convention based on activation
record. Despite the different approach to handle local state and
calls, we are still able to show a similar property to that of
\texttt{f1}. This illustrates that the logical relation is not
specific to the stack-based calling convention as it can be used to
reason about programs that follow a different calling convention.
\begin{figure}[htbp]
  \centering
\begin{lstlisting}
f2: malloc $r_l$ 1
    store $r_l$ 1
    fetch $r_1$ $\adv$
    call $r_1$($[]$,$[r_l]$)
    assert $r_l$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a calling convention not relyant
    on the stack}
  \label{fig:prog-f2}
\end{figure}

\subsection{Well-bracketed control-flow}
